\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-10-09 draft.tex
make hypertargets to propositions from proofs work
search draft for 'break', change to renewal

The lobby chooses its level of effort as a function of the trade agreement tariffs and the antidumping duties, given the implications of that choice on the government agency's probability of breaking the agreement. In effect, the lobby maximizes probability-weighted profits net of effort:
\[
  \max_{e} r(e,\bta,\tad) \pi(\tau^{ad}) + [1 - r(e,\bta,\tad)] \pi(\tau^a) - e
\]
The first order condition shows that the lobby balances the cost of an extra dollar of expenditure with the higher profits from anti-dumping duties weighted by the increase in the probability of receiving the extension of the antidumping duties:
\begin{equation}
	\frac{\partial r(e,\bta,\tad)}{\partial e} \left[ \pi(\tau^{ad})  - \pi(\tau^a) \right] = 1 
	\label{eq:lobbyfoc}
\end{equation}
Result~\ref{res:bincC} below and the fact that antidumping duties are necessarily larger than trade agreement tariffs ensure the second order condition. To guarantee an interior solution, we need
  \begin{equation}
	  \frac{\partial r(0,\bta,\tad)}{\partial e} \left[ \pi(\tau^{ad}) - \pi(\tau^a) \right] > 1.
		\label{ine:lobint}	
  \end{equation}
It may be that either the antidumping duty is too low or the marginal impact of the first lobbying dollar is too small for it to be in the lobby's interest to exert effort. The main results of the paper only hold when the marginal impact of the first lobbying dollar on the renewal probability is sufficiently high to make engaging in the political process worthwhile for the lobby.

@@

Let's look first at the direct effect of changing $\tau^a$ on the renewal probability. For any effort level $e$, when the trade agreement tariff is very low, only a small set of realizations of $\ta$ associated with the lowest values of $\ga(e,\ta)$ will lead to approval of the trade agreement, implying a high break probability. As the trade agreement tariff rises, larger values of $\ga(e,\ta)$ are consistent with approving the trade agreement, so the set of $\ta$'s that lead to trade agreement approval is larger. That is, the break probability decreases as $\tau^a$ increases.

\begin{lemma}
  The direct effect of the home trade agreement tariff on the probability the government renews the antidumping duty is negative.
  \label{res:leg_a}
\end{lemma}

@@

\begin{lemma}
  Lobbying effort is weakly decreasing in trade agreement tariffs.
  \label{res:lobby}
\end{lemma}

Turning to the second component of the indirect effect, it's useful to note that lobbying affects only the weight the government agency places on the profits of the import-competing industry. These profits are higher under antidumping duties than under the trade agreement tariff. Assumption~\ref{as:ga_c} implies that the government becomes more favorably inclined---albeit at a decreasing rate---toward the higher antidumping duties and associated profits as lobbying increases and thus more likely to break the trade agreement.

\begin{lemma}
  The probability that the government agency renews the antidumping duties is increasing and concave in lobbying effort $\left(\text{i.e. } \frac{\partial r}{\partial e} \geq 0, \ \frac{\partial^2 r}{\partial e^2} \leq 0  \right)$.
  \label{res:bincC}
\end{lemma}

@@

\begin{result}
	The total probability that the antidumping duties will be renewed is decreasing in $\tau^a$ (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \tau^a} \leq 0$).
	\label{res:bcomB}
\end{result}

@@

Turning to the effect of the foreign trade agreement tariffs on the probability that the antidumping duties will be renewed, it is perhaps not surprising that there is no effect:
\begin{result}
  The total probability that the antidumping duties will be renewed is constant in the foreign trade agreement tariff.
  \label{res:leg_astar}
\end{result}

@@

\begin{lemma}
  The direct effect of exogenous positive shifts in the political weighting function $\ga(\cdot,\ta)$ on the probability the government renews the antidumping duty is positive.
	  \label{res:eg}
\end{lemma}

@@

\begin{lemma}
  The direct effect of an increase in the import competing sector's profitability on the probability the government renews the antidumping duty is positive.
  \label{res:pi_dir}
\end{lemma}

\begin{lemma}
  Lobbying effort is weakly increasing in the import competing sector's profitability.
  \label{res:pi_indir}
\end{lemma}

\begin{result}
	The total probability that the antidumping duties will be renewed is increasing in $\pi$. (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \pi} \geq 0$).
	\label{res:pi_total}
\end{result}

@@

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the break probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive. Labeling the numerator of that expression $Z(\bta,\tad)$, the derivative of this quantity with respect to $\tau^{a}$ is 
\begin{equation}
  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\bta,\tad) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:a}
\end{equation}

@@

@@

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the break probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive. Labeling the numerator of that expression $Z(\bta,\tad)$, the derivative of this quantity with respect to $\tau^{a}$ is 
\begin{equation}
  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\bta,\tad) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:pi}
\end{equation}

>>>>

The lobby chooses its level of effort as a function of the trade agreement tariffs and the antidumping duties, given the implications of that choice on the government agency's probability of renewing the duties. In effect, the lobby maximizes probability-weighted profits net of effort:
\[
  \max_{e} r(e,\bta,\tad) \pi(\tau^{ad}) + [1 - r(e,\bta,\tad)] \pi(\tau^a) - e
\]
The first order condition shows that the lobby balances the cost of an extra dollar of expenditure with the higher profits from anti-dumping duties weighted by the increase in the probability of receiving the extension of the antidumping duties:
\begin{equation}
	\frac{\partial r(e,\bta,\tad)}{\partial e} \left[ \pi(\tau^{ad})  - \pi(\tau^a) \right] = 1 
	\label{eq:lobbyfoc}
\end{equation}
Result~\ref{res:bincC} below and the fact that antidumping duties are necessarily larger than trade agreement tariffs ensure the second order condition. To guarantee an interior solution, we need
  \begin{equation}
	  \frac{\partial r(0,\bta,\tad)}{\partial e} \left[ \pi(\tau^{ad}) - \pi(\tau^a) \right] > 1.
		\label{ine:lobint}	
  \end{equation}
It may be that either the antidumping duty is too low or the marginal impact of the first lobbying dollar is too small for it to be in the lobby's interest to exert effort. The main results of the paper only hold when the marginal impact of the first lobbying dollar on the renewal probability is sufficiently high to make engaging in the political process worthwhile for the lobby.

@@

Let's look first at the direct effect of changing $\tau^a$ on the renewal probability. For any effort level $e$, when the trade agreement tariff is very low, only a small set of realizations of $\ta$ associated with the lowest values of $\ga(e,\ta)$ will lead to the antidumping duties being re-approved, implying a high renewal probability. As the trade agreement tariff rises, larger values of $\ga(e,\ta)$ are consistent with approving the trade agreement, so the set of $\ta$'s that lead to trade agreement approval is larger. That is, the renewal probability decreases as $\tau^a$ increases.

\begin{lemma}
  The direct effect of the home trade agreement tariff on the probability the government renews the antidumping duty is negative. \hyperlink{Pr_leg_a}{Proof}
  \label{res:leg_a}
\end{lemma}

@@

\begin{lemma}
  Lobbying effort is weakly decreasing in trade agreement tariffs. \hyperlink{Pr_lobby}{Proof}
  \label{res:lobby}
\end{lemma}

Turning to the second component of the indirect effect, it's useful to note that lobbying affects only the weight the government agency places on the profits of the import-competing industry. These profits are higher under antidumping duties than under the trade agreement tariff. Assumption~\ref{as:ga_c} implies that the government becomes more favorably inclined---albeit at a decreasing rate---toward the higher antidumping duties and associated profits as lobbying increases and thus more likely to renew the antidumping duties.

\begin{lemma}
  The probability that the government agency renews the antidumping duties is increasing and concave in lobbying effort $\left(\text{i.e. } \frac{\partial r}{\partial e} \geq 0, \ \frac{\partial^2 r}{\partial e^2} \leq 0  \right)$. \hyperlink{Pr_bincC}{Proof}
  \label{res:bincC}
\end{lemma}

@@

\begin{result}
	The total probability that the antidumping duties will be renewed is decreasing in $\tau^a$ (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \tau^a} \leq 0$). \hyperlink{Pr_bcomB}{Proof}
	\label{res:bcomB}
\end{result}

@@

Turning to the effect of the foreign trade agreement tariffs on the probability that the antidumping duties will be renewed, it is perhaps not surprising that there is no effect:
\begin{result}
  The total probability that the antidumping duties will be renewed is constant in the foreign trade agreement tariff. \hyperlink{Pr_astar}{Proof}
  \label{res:leg_astar}
\end{result}

@@

\begin{lemma}
  The direct effect of exogenous positive shifts in the political weighting function $\ga(\cdot,\ta)$ on the probability the government renews the antidumping duty is positive. \hyperlink{Pr_eg}{Proof}
	  \label{res:eg}
\end{lemma}

@@

\begin{lemma}
  The direct effect of an increase in the import competing sector's profitability on the probability the government renews the antidumping duty is positive. \hyperlink{Pr_pi_dir}{Proof}
  \label{res:pi_dir}
\end{lemma}

\begin{lemma}
  Lobbying effort is weakly increasing in the import competing sector's profitability. \hyperlink{Pr_pi_indir}{Proof}
  \label{res:pi_indir}
\end{lemma}

\begin{result}
	The total probability that the antidumping duties will be renewed is increasing in $\pi$. (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \pi} \geq 0$). \hyperlink{Pr_pi_total}{Proof}
	\label{res:pi_total}
\end{result}

@@

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the renewal probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive. Labeling the numerator of that expression $Z(\bta,\tad)$, the derivative of this quantity with respect to $\tau^{a}$ is 
\begin{equation}
  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\bta,\tad) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:a}
\end{equation}

@@

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_eg}{Proof of Result~\ref{res:eg}}}: \\

@@

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to a positive shift in the $\pi(\cdot)$ function; to show that the renewal probability is increasing in such a positive shift, I must demonstrate that this derivative is negative. The derivative is 
\begin{equation}
  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\bta,\tad) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:pi}
\end{equation}
